Evaluating urban greening scenarios for urban heat mitigation: a spatially-explicit approach

### 2020-12-09 reports/article.tex
data materials from Zenodo

\section*{Acknowledgments}
This research has been supported by the \'Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL).

>>>>

\section*{Data availability statement}

The data required to reproduce the results is available at \url{https://zenodo.org/record/4316572}. A repository with the code materials and detailed instructions of the steps to reproduce the results is available at \url{https://github.com/martibosch/lausanne-greening-scenarios}

\section*{Acknowledgments}
This research has been supported by the \'Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL).
The authors received no specific funding for this work.
